\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-16 evaluation.tex

For the vNext case study, the random scheduler was able to reproduce the bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in Section~\ref{} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

>>>>

For the vNext case study, the random scheduler was able to reproduce the bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in Section~\ref{sec:psharp:testing} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

### 2015-09-16 experience.tex

The main system that we tested is \emph{CScale}~\cite{X},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
A key challenge was that
CScale contains inter-service communication.
%\PTComment{Cut: detail.}
% that resolves services
% via Fabric but communicates
% using a non-Fabric remote procedure call protocol.
To close the system,
%\PTComment{Cut: we implemented service resolution}
% we first implemented service resolution in our Fabric model,
% which resolves Fabric service names to IP addresses.
%We then replaced 
we 
replaced the relevant classes
% replaced the inter-service communication classes with our own,
% ;
% our replacement includes the ability to map
% URLs to \psharp{} machines
so that remote procedure calls are implemented
by sending and receiving \psharp{} events.
Thus,
we converted a distributed system
that uses both Fabric and its own
network communication protocol
% that runs on the Fabric platform
% and 
% uses network communication
into 
a closed single process system. 
% that uses multiple threads,
% contains
% the Fabric model
% and the CScale services,
% and does not use network communication.
%\PTComment{Cut: we had to remove static fields.}
% Additional changes were needed to
% remove certain static (per-process) fields,
% as these were inadvertently
% being shared between services
% after making the system a single process.
A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However,
we were able to find a \texttt{NullReferenceException}
bug
in CScale
by running it on our model.

>>>>

The main system that we tested is 
\emph{CScale}~\cite{faleiro2012},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
A key challenge was that
CScale contains inter-service communication.
%\PTComment{Cut: detail.}
% that resolves services
% via Fabric but communicates
% using a non-Fabric remote procedure call protocol.
To close the system,
%\PTComment{Cut: we implemented service resolution}
% we first implemented service resolution in our Fabric model,
% which resolves Fabric service names to IP addresses.
%We then replaced 
we 
replaced the relevant classes
% replaced the inter-service communication classes with our own,
% ;
% our replacement includes the ability to map
% URLs to \psharp{} machines
so that remote procedure calls are implemented
by sending and receiving \psharp{} events.
Thus,
we converted a distributed system
that uses both Fabric and its own
network communication protocol
% that runs on the Fabric platform
% and 
% uses network communication
into 
a closed single process system. 
% that uses multiple threads,
% contains
% the Fabric model
% and the CScale services,
% and does not use network communication.
%\PTComment{Cut: we had to remove static fields.}
% Additional changes were needed to
% remove certain static (per-process) fields,
% as these were inadvertently
% being shared between services
% after making the system a single process.
A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However,
we were able to find a \texttt{NullReferenceException}
bug
in CScale
by running it on our model.

### 2015-09-16 overview.tex

We argue that our approach is \emph{flexible} since it allows the user to model \emph{as much} or \emph{as little} of the environment as required to achieve the desired level of testing. We also argue that our approach is \emph{generic} since a programmer can build on top of it to test other distributed systems besides vNext (see Section~\ref{sec:exp}). Furthermore, the language features that are required to be used to connect the real code with the modeled code, are already being heavily used in production for testing purposes (e.g. \emph{virtual method dispatch}), which significantly lowers the bar for product groups to embrace \psharp for testing.

@@

One can imagine a liveness monitor as a \emph{thermometer}: as the program executes and the liveness property is not satisfied, the liveness monitor stays in the hot state, which infinitely raises the temperature. If the liveness property is ever satisfied, and thus the liveness monitor transitions to a cold state, the temperature is instantly reduced to normal levels. Encoding liveness properties using hot and cold states enables the programmer to specify arbitrary LTL properties. The liveness monitors in \psharp are based on previous work~\cite{?}.

\subsection{Systematic testing}
In this section, we present more specifics of how the \psharp bug-finding runtime works and extensions that we did since the original work~\cite{deligiannis2015psharp} to be able to use \psharp to systematically test production code.

>>>>

We argue that our approach is \emph{flexible} since it allows the user to model \emph{as much} or \emph{as little} of the environment as required to achieve the desired level of testing. We also argue that our approach is \emph{generic} since a programmer can build on top of it to test other distributed systems besides vNext (see Section~\ref{sec:cases}). Furthermore, the language features that are required to be used to connect the real code with the modeled code, are already being heavily used in production for testing purposes (e.g. \emph{virtual method dispatch}), which significantly lowers the bar for product groups to embrace \psharp for testing.

@@

One can imagine a liveness monitor as a \emph{thermometer}: as the program executes and the liveness property is not satisfied, the liveness monitor stays in the hot state, which infinitely raises the temperature. If the liveness property is ever satisfied, and thus the liveness monitor transitions to a cold state, the temperature is instantly reduced to normal levels. Encoding liveness properties using hot and cold states enables the programmer to specify arbitrary LTL properties. The liveness monitors in \psharp are based on previous work~\cite{Desai:EECS-2015-198}.

\subsection{Systematic testing}
\label{sec:psharp:testing}
In this section, we present more specifics of how the \psharp bug-finding runtime works and extensions that we did since the original work~\cite{deligiannis2015psharp} to be able to use \psharp to systematically test production code.
